workshop

### 2022-09-16 scripts/workshop/workshop.Rmd
Update workshop.Rmd

```{r}
data <- read_csv(here("raw_data/weighted_prev_competence_111220.csv"))
tree <- ape::read.nexus(here("raw_data/asup_just_tree.txt"))
names <- read_csv(here("raw_data/species_names_ids.csv"))
```

@@

>>>>

```{r}
data <- read_csv(here("data/weighted_prev_competence_111220.csv"))
tree <- ape::read.nexus(here("data/raw_data/asup_just_tree.txt"))
names <- read_csv(here("data/raw_data/species_names_ids.csv"))
```

@@

## Variation in competence for each species

```{r}
species_comp <- data %>% group_by(Species) %>% summarize(mean = mean(SQMean),
                                                         var = var(SQMean),
                                                         se = sqrt(var(SQMean)/n()))

species_comp %>% ggplot(.,aes(x=Species, y=mean)) + geom_point() + geom_linerange(aes(ymin=mean-se,ymax=mean+se))
```
